\documentclass{bmd2019a}

\begin{document}

\begin{flushleft}
{\fontsize{16pt}{20pt}\selectfont%
  Expanded Optimization for Discovering\\}
{\fontsize{16pt}{20pt}\selectfont%
  Optimal Lateral Handling Bicycles}
\end{flushleft}

%%%%%%%%%%%%%%%% authors %%%%%%%%%%%%%%%
\begin{flushleft}
  {\fontsize{12}{14}{Jason K. Moore, Mont Hubbard, and Ronald A. Hess}\\}
  \textit{Mechanical and Aerospace Engineering\\
          University of California, Davis\\
          One Shields Avenue, Davis, CA, USA 95817\\
          e-mail: jkm@ucdavis.edu, mhubbard@ucdavis.edu, rahess@ucdavis.edu}
\end{flushleft}

\section*{Abstract}
%
Physical design features of ground vehicles can affect their lateral handling
qualities. The geometry, mass, mass distribution, of the vehicle's primary
components and tire characteristics are primary contributors to poor and good
handling due to their important influence on the vehicle's dynamics. In past
work, we have presented a theoretical and computational framework for assessing
the lateral task-independent handling qualities of simplified single track
vehicle designs~\cite{Hess2012,Moore2012}. It subsequent work, we have shown
that minimizing the HQM can produce theoretically optimal handling designs with
just four geometric parameters are explored as the optimization
variables~\cite{Moore2016}. The present work's goal is to expand this
optimization problem to 24 geometry, mass, and inertial parameters as the
optimization variables so that a broader search space of optimal bicycle
designs is considered. This task is complicated by the fact that we desire to
limit the search space to physically realizable bicycle designs. Doing so
introduces 35 linear and non-linear constraint equations on the optimization
variables. We formulate a constrained optimization problem and use nonlinear
programming to discover optimal, yet realizable, bicycle designs.

Our formulation exposes 24 optimization variables
$\mathbf{p}\in\mathbb{R}^{24}$ that are both reformulations of and additions to
the parameters of the benchmark bicycle~\cite{Meijaard2007}. We separate the
rider's inertial parameters from the rear frame of the bicycle for the purposes
of rider/bicycle relative configuration but do not introduce any more than the
benchmark's four rigid bodies. The variables are as follows;
%
\begin{itemize}
  \itemsep-0.25em
  \item wheelbase, trail, steer axis tilt, wheel radii
  \item somersault angle of the person (same direction as the bicycle pitch)
  \item mass of each of the front frame, rear frame, front wheel, and rear wheel
  \item mass center of the front frame, rear frame, and rider
  \item principal central radii of gyration of both the front and rear frames
  \item principal inertia pitch angle of the front frame, rear frame, and rider
\end{itemize}

We formulate a bounds on the variables as well as linear and nonlinear
constraints among the variables to ensure a physically realizable bicycle.
Below the constraints are defined and grouped by the associated rigid body or
collection thereof:
%
\begin{description}

  \item[Vehicle] The resulting combination of the five rigid bodies.
    \begin{itemize}
      \itemsep0em
      \item The physical extents of the bicycle and rider must exist above the
        ground plane.
      \item The bicycle and rider are symmetric about the rider's sagittal
        plane.
      \item The mass of each bicycle rigid body is positive and greater than a
        minimum value and the total below a reasonably lift-able amount.
      \item The wheels cannot overlap, i.e. wheelbase > front radius + rear
        radius.
      \item The bicycle cannot topple forward during hard braking or backward
        during hard acceleration, i.e. -g < acceleration < g.
    \end{itemize}

  \item[Wheels] Both the front and rear wheels have the same constraints.
    \begin{itemize}
      \itemsep0em
      \item The radius must be greater than a minimum value.
      \item The bicycle wheels should be inertially wheel-like, i.e.
        $I_{rot}=mr^2, I_{rad}=I_{rot}/2$.
    \end{itemize}

  \item[Frames] Both the front and rear frames have the same constraints.
    \begin{itemize}
      \itemsep0em
      \item We limit a pair of principal directions to lie in the roll/yaw
        plane and that one of the axes must be within $\pm \pi/4$ with respect
        to the ground plane.
      \item We require the mass and inertia of the frames to be positive and of
        large enough values to be constructed from materials in a space frame
        of a specified minimal density.
      \item We enforce that the body is of a planar nature, i.e.
        $k_{lateral}^2=k_{longitudinal}^2+k_{vertical}^2$, where $k$ is the
        radius of gyration.
    \end{itemize}

  \item[Rider] A single rigid body representing the rider.
    \begin{itemize}
      \itemsep0em
      \item The mass of the rider is that of an average person.
      \item The rider's joint angles are in a fixed nominal configuration that
        is typical for upright bicycling and the resulting mass distribution of
        the rider is derived from standard body segment estimation methods.
      \item One principal axis must be parallel with the bicycle's pitch axis.
    \end{itemize}

\end{description}

The constraint statements above translate into upper and lower bounds on 12 of
the 24 variables $\mathbf{p}^U,\mathbf{p}^L$ and 14 linear and 21 nonlinear
constraints among the variables $\mathbf{g}(\mathbf{p})$ and thus can be
expressed in the standard non-linear programming form.
%
\begin{equation}
  \begin{aligned}
    & \underset{\mathbf{p}}{\text{minimize}} & & max(\textrm{HQM}(\mathbf{p})) \\
    & \text{subject to} & & \\
    & & & \mathbf{g}^L \leq \mathbf{g}(\mathbf{p}) \leq \mathbf{g}^U \\
    & & & \mathbf{p}^L \leq \mathbf{p} \leq \mathbf{p}^U \\
  \end{aligned}
\end{equation}

We make use of the interior-point optimizer IPOPT~\cite{Wachter2006} to find
solutions to this nonlinear programming problem at variety of bicycle speeds
and will present the resulting discovered optimal bicycle designs in the full
conference paper.

\bibliographystyle{acm}
\bibliography{BMD2019}

\end{document}
